---
title: "Linear Models"
author: "Jenna Mohammed"
date: '2023-11-09'
output: html_document
---

the way predictors are related to outcome is through the formula 
- not a perfect fit, some errors are stacked upon (mean 0 and variance sigma^2)
- continuous added directly, categorical required dummy variable
```{r}
library(tidyverse)
library(p8105.datasets)
```

```{r}
# loading and cleaning data 

data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough != "Staten Island") |> 
  select(price, stars, borough, neighborhood, room_type)
```

let's fit a model!!

```{r}

# linear regression model ; start with the dataframr

#fit = 
 # nyc_airbnb |>
  #lm(price ~ stars + borough, data = nyc_airbnb)

# lm -> formula is the first thing in the function, not the dataframe
```

let's look at the `fit`

```{r}
#summary(fit)
summary(fit)$coef
fitted.values(fit)

#^ not used often
```

tidy up the output
```{r}
fit |>
  broom ::glance()

# broom/glance -> high level summary of how well this function works
# better option
```

tidy up the coefficients 
```{r}
fit |>
  broom::tidy()

# best option to use

fit |> 
  broom::tidy() |> 
  select(term, estimate, p.value) |> 
  mutate(term = str_replace(term, "^borough", "Borough: ")) |> 
  knitr::kable(digits = 3)

# shows a neat and tidy table
```

## quick look at diagnostics 

```{r}
nyc_airbnb|>
  modelr::add_residuals(fit) |>
  ggplot(aes(x = resid)) +
  geom_density() +
  xlim(-100, 500)

nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = borough, y = resid)) + geom_violin()

nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = stars, y = resid)) + geom_point()
```

## Hypothesis Test for categorical predictor 

fot a "null" and "alternative" model

```{r}
# hypothesis testing for categorical ->

fit |>
  broom::tidy()

fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough + room_type, data = nyc_airbnb)

anova(fit_null, fit_alt) |> 
  broom::tidy()

# can use anove as long as you have a fit 
```

## Borough-level differences

```{r}

```


```{r}
```

